---
title: "Articles, Tutorials, and Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    includes:
      before_body: [include_header_navpage.html]
---
### Intersting analysis done, involving techniques and approaches from data science, statistics, machine learning, and artificial intelligence. To learn more about me, check out the [About](./about.html) page.

***

## [Viridis Demo](./1-example.html)
```{r include = FALSE}
library(viridis)
```

The code below demonstrates two color palettes in the [viridis](https://github.com/sjmgarnier/viridis) package. Each plot displays a contour map of the Maunga Whau volcano in Auckland, New Zealand.

### Viridis colors

```{r}
image(volcano, col = viridis(200))
```

[... See More](./1-example.html)

***

## [Sustainability Dashboard](./4-shiny-dash.html)
Interactive web application built with R and Shiny, showing energy usage, emissions, water, and sustaibility projects at Montana State University.

[... See More](./4-shiny-dash.html)